Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-27 analysis.tex
fixme at the top
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@710 ccdd05d5-56c1-461a-bf98-85f6876523b4
caption
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@717 ccdd05d5-56c1-461a-bf98-85f6876523b4
added flop budget
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@740 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added new diagram to paper
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@764 ccdd05d5-56c1-461a-bf98-85f6876523b4

@@

\begin{comment}

% Ugly diagram!

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=1.0\textwidth]{figures/flow_chart.pdf}
\caption{\label{f:flowchart} 
}
\end{center}
\end{figure*}

\end{comment}

>>>>

\FIXME{
I would like to see this section have more of a description of the
pipeline and a figure representing it.
}

@@

\begin{figure}
	\includegraphics{figures/lloid-diagram.pdf}
	\caption{Schematic of LLOID pipeline illustrating signal flow.  Circles with arrows represent upsampling \protect\includegraphics{figures/upsample-symbol.pdf} or downsampling \protect\includegraphics{figures/downsample-symbol.pdf}.  Circles with plus signs represent summing junctions \protect\includegraphics{figures/adder-symbol.pdf}.  Squares \protect\includegraphics{figures/fir-symbol.pdf} stand for FIR filters.  Sample rate decreases from the top of the diagram to the bottom.}
\end{figure}

### 2011-05-27 figures/diagram.tex
Added new diagram to paper
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@764 ccdd05d5-56c1-461a-bf98-85f6876523b4

\documentclass{amsart}
\usepackage[usenames]{color}
\usepackage{tikz}
\usepackage{signalflowdiagram}
\usetikzlibrary{fit,calc,chains,scopes}
\begin{document}

@@

\begin{figure}
	\begin{center}
		\begin{tikzpicture}[
			node distance=2mm,
			every path/.style={line width=1pt},
			every node/.style={line width=1pt}
		]
			\foreach \x in {0,1,2} {
				\node[draw] at (0, {\x == 0 ? 0cm : (\x == 1 ? -3cm : -7.5cm)}) (u0) {};
				\node[draw, below=of u0] (u1) {};
				\node[below=of u1] (uellip\x) {$\vdots$};
				\node[draw, below=of uellip\x] (u2) {};

@@

		\end{tikzpicture}
		\caption{Schematic of LLOID pipeline illustrating signal flow.  Circles with arrows represent upsampling \protect\tikz{\protect \node[resample] {\tiny$\uparrow$};} or downsampling \protect\tikz{\protect \node[resample] {\tiny$\downarrow$};}.  Circles with plus signs represent summing junctions \protect\tikz{\protect \node[line width=1pt,adder] {\tiny$\uparrow$};}.  Squares \protect\tikz{\protect \node[line width=1pt,draw] {};} stand for FIR filters.  Sample rate decreases from the top of the diagram to the bottom.}
	\end{center}
\end{figure}

This diagram is a work in progress.  Some corrections to make:

{\color{red}
\begin{itemize}
\item Add delay lines.
\item Switch first downsampler and whitener.
\item Resamplers are connected in series, not parallel.
\item Translate figure to the left to align it visually with the caption.
\end{itemize}
}

>>>>

\documentclass{amsart}
\usepackage{tikz}
\usepackage{signalflowdiagram}
\usetikzlibrary{external,fit,calc,chains,scopes}
\tikzexternalize
\begin{document}

@@

\tikzsetnextfilename{lloid-diagram}
\begin{tikzpicture}[
	node distance=2mm,
	every path/.style={line width=1pt},
	every node/.style={line width=1pt}
]
	\foreach \x in {0,1,2} {
		\node[draw] at (0, {\x == 0 ? 0cm : (\x == 1 ? -3cm : -7.5cm)}) (u0) {};
		\node[draw, below=of u0] (u1) {};
		\node[below=of u1] (uellip\x) {$\vdots$};
		\node[draw, below=of uellip\x] (u2) {};

@@

\end{tikzpicture}

\tikzsetnextfilename{upsample-symbol}
\begin{tikzpicture}
	\node[resample] {\tiny$\uparrow$};
\end{tikzpicture}

\tikzsetnextfilename{downsample-symbol}
\begin{tikzpicture}
	\node[resample] {\tiny$\downarrow$};
\end{tikzpicture}

\tikzsetnextfilename{adder-symbol}
\begin{tikzpicture}
	\node[line width=1pt,adder] {};
\end{tikzpicture}

\tikzsetnextfilename{fir-symbol}
\begin{tikzpicture}
	\node[line width=1pt,draw] {};
\end{tikzpicture}
